### 2011-01-05 proof.pre.tex
Start using the munger; make overrides a separate file
Use munger to improve the model description

\documentclass{article}
\usepackage{holtexbasic}
\usepackage{alltt}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}
\section*{Introduction}
First, a warning about one quirky convention.
When I write $\sum_{m=0}^b (f m)$ I mean for the variable $m$ to range from $0$ up to but \emph{not including} $b$.

@@

\section*{The Model}
\begin{description}
\item[Global Parameters:]\hfill
\begin{itemize}
\item
     the width of every slice, encoded as the index, w, of the last shift register
\item
     the input series, input.
\end{itemize}
\item[Each slice has:]\hfill
\begin{itemize}
\item
     w+1 shift registers, named SR 0, SR 1, ..., SR w;
\item
     an output register.
\end{itemize}
\item[Each SR has a source]\hfill
\begin{itemize}
\item
     The source for SR 0 of slice 0 is the global input.
\item
     The source for SR 0 of slice (SUC n) is the output of slice n.
\item
     The source for SR (SUC m) is SR m of the same slice.
\end{itemize}
\item[Each slice updates periodically]\hfill
\begin{itemize}
\item
     Slice n updates at time t iff ∃x. n + ((SUC x) * ((SUC w) ** n))
\item
   At time 0, all shift registers have value 0.
\item
   At each update time for its slice, a SR gets the value of its source at the previous time.
\item
   The output of a slice at some time is the sum of its shift registers at the same time.
\end{itemize}
\end{description}
\section*{Some Small Lemmas}
\input{SRLastUpdateProof.tex}
\input{SRFirstProof.tex}
\input{SR0UntilProof.tex}
\section*{Major Lemma 1}
\input{OutputFirstProof.tex}
\section*{Major Lemma 2}
\input{OutputSourceProof.tex}
\section*{Main Theorem}
\input{SumInChunksProof.tex}
\input{OutputInputProof.tex}
\end{document}

>>>>

\documentclass{article}
\usepackage{holtexbasic}
\usepackage{alltt}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}
\section*{Introduction}
First, a warning about one quirky convention.
When I write \HOLtm{SIGMA (\m. f m) (count b)} I mean for the variable $m$ to range from $0$ up to but \emph{not including} $b$.

@@

\section*{The Model}
\begin{description}
\item[Global Parameters:]\hfill
\begin{itemize}
\item
     the width of every slice, encoded as the index, \HOLtm{p.w}, of the last shift register;\\
     the total number of shift registers is \HOLtm{SUC p.w = p.w + 1};
\item
     the input series, \HOLtm{p.input}.
\end{itemize}
\item[Each slice has:]\hfill
\begin{itemize}
\item
     \HOLtm{SUC p.w} shift registers, named \HOLtm{SR p n 0}, \HOLtm{SR p n 1}, ..., \HOLtm{SR p n p.w};
\item
     an output register \HOLtm{output n}.
\end{itemize}
\item[Each SR has a source]\hfill
\begin{itemize}
\item
     The source for \HOLtm{SR p 0 0} of slice \HOLtm{0} is the global input.
\item
     The source for \HOLtm{SR p (SUC n) 0} of slice \HOLtm{SUC n} (the output of slice \HOLtm{n}).
\item
     The source for \HOLtm{SR p (SUC n) (SUC m)} is \HOLtm{SR p (SUC n ) m} (of the same slice).
\end{itemize}
\item[Each slice updates periodically]\hfill
\begin{itemize}
\item
     Slice \HOLtm{n} updates at time \HOLtm{t} if and only if \HOLtm{∃x. t = n + ((SUC x) * ((SUC p.w) ** n))}
\item
   At time \HOLtm{0}, all shift registers have value \HOLtm{0}.
\item
   At each update time for its slice, a SR gets the value of its source at the previous time.
\item
   The output of a slice at some time is the sum of its shift registers at the same time.
\end{itemize}
\end{description}

This is all summarized by the folowing theorems.
\begin{alltt}
\HOLthm[alltt]{simplified.update_time_def}
\HOLthm[alltt]{simplified.Slice_def}
\end{alltt}
\section*{Some Small Lemmas}
\input{SRLastUpdateProof.tex}
\input{SRFirstProof.tex}
\input{SR0UntilProof.tex}
\section*{Major Lemma 1}
\input{OutputFirstProof.tex}
\section*{Major Lemma 2}
\input{OutputSourceProof.tex}
\section*{Main Theorem}
\input{SumInChunksProof.tex}
\input{OutputInputProof.tex}
\end{document}
